---
name: Julian Cabezas
position: "Environmental Data Science Consultant"
address: "Adelaide, Australia"
phone: +61 484190364
www: www.juliancabezas.com
email: "juliancabzas@gmail.com"
github: juliancabezas
linkedin: juliancabezas
aboutme: "Data science, REDD+, GIS, Remote Sensing, R and Python Programming"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "414141"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(tinytex)
if(!tinytex:::is_tinytex()) tinytex::install_tinytex()

```
<!-- # Perfil Profesional -->

<!-- My way of working is based on the capability to face complex challanges regarding analyzing data from several sources, generating algorithms to analize social, economic and environmental data, with a focus on spatially explicit information. I work as consultant, full-time professional or researcher. As part of my job, I have generated multiple scientific publications and working papers, with the intention of sharing methodologies and approaches. -->

# Education

```{r education}
library(vitae)

edu <- data.frame("Titulo"=c("Renewable Natural Resources Engineer","Master of Data Science (Current student)"),
              "Cuando"=c("2010-2015","2020-2021"),
              "Ins"=c("University of Chile","University of Adelaide"),
              "Donde"=c("Santiago, Chile","Adelaide, Australia"))

  detailed_entries(edu,
    what = Titulo,
    when = Cuando,
    with = Ins,
    where = Donde
  )
```

# Professional skills

 * Developmemt and implementation of spatial and statistic data analysis and machine learning algorithms.
 * Estimation of forest carbon emissions for REDD+ reports.
 * Processing of optical satellite and UAV data.
 * Advanced R and Python programming skills.
 * Advanced skills in GIS and remote sensing softwares: ArcGIS 10.4, ENVI 5.1  and QGIS.
 * UAV Driving: experience with Mikrokopter Okto XL and DJI Phantom 4 Pro models.
 * Chilean driver licence (Class B).
 * **Languages**: Native Spanish, Advanced English (score 7.5/9 in academic IELTS)., Basic German


# Professional Experience

```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
   "Consultant", "The Mullion Group", "Canberra, Australia", "2020-2021", "Implementation of the Generic Carbon Budget Model (GCBM) for the estimation of REDD+ carbon emissions and removals in Chile",
  "National Project Personnel for the Unit of Climate Change and Environmental Services, National Forestry Corporation (CONAF)", "Food and Agriculture Organization of the United Nations (FAO)", "Santiago, Chile", "2019", list("Support for the Monitoring and Measurement System of the National Strategy of Climate Change and Vegetation Resources", "REDD+ Technical Annex elaboration and reviewing process"),
  "Statistical Analyst", "R&D Department - National Institute of Statistics", "Santiago, Chile", "2018 - 2019", list("Development of statistic analysis algorithms in national survey data"," Implementation of text mining algorithms for automatic classification of labor sector in national surveys"),
  "Remote Sensing Scientist", "Karlsruhe Institute of Technology (KIT)", "Karlsruhe, Germany", "2016 - 2017", "Implementation of disturbance detection algorithms BFAST and LandtrendR on Landsat time series data (SaMovar Project)",
    "GIS assistant", "University of Chile", "Santiago, Chile", "2015", "GIS elaborations and spatial analysis in the Study for the definition of protection areas in the east piedmont of Santiago project, financed by the United Nations Development Programme (UNDP) "
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Consultancy

 * **2017**: Report elaboration and participation as expert witness in the case D-33-2017 of the environment court of Santiago. with the report “Spatio-temporal analysis of causality and spatial extent of the Nilahue Barahona fire in January 2017".
 * **2017**: Report for the Forest Institute of Chile (INFOR): “Delineation and classification of water courses in forest basins in southern Chile: Analysis using remote sensing techniques" (forest and water research line)
 * **2014**: GIS advisor: Diagnosis of the agricultural and soil system of the area of influence of the Carén reservoir. Ambiente Seguro-CODELCO El Teniente. Mapping and analysis of land uses.

# Academic achievements

## International journals

 *	**Cabezas**, J., Galleguillos M. & J. Pérez-Quezada. (2016). A method to predict vascular plant richness in a heterogeneous wetland using spectral and textural features and a random forest algorithm. IEEE Geoscience and Remote Sensing Letters 13(5): 646-650.
 *	**Cabezas**, J., Galleguillos, M., Valdés, A., Fuentes, J.P., Pérez, C. & J. Pérez-Quezada. (2015). Impacts of management on vegetation and carbon stocks in an anthropogenic peatland using field and remote sensing data. Ecosphere 6(12): 282.
 *	Pérez-Quezada, J. F., Brito, C. E., **Cabezas**, J., Galleguillos, M., Fuentes, J. P., Bown, H. E., & Franck, N. (2016). How many measurements are needed to estimate accurate daily and annual soil respiration fluxes? Analysis using data from a temperate rainforest. Biogeosciences, 13(24), 6599.
 
## Book Chapters

 *	Pérez-Quezada J., Astorga B., **Cabezas** J., Labra F. & Rovira J. Ecologic Planning of the territory applied in the piedmont of Santiago. (2018) In: Pérez-Quezada J. y Rodrigo P. (Eds.) Applied methodologies for the conservation of the biodiverity of Chile. Environmental Sciences Series N°1. Faculty of Agricultural Sciences, University of Chile, Santiago: 379-411 (Original in Spanish)
 
## Presentations in scientific congresses

 *	**Cabezas**, J & F. Fassnacht (2018). Reconstructing the vegetation disturbance history of a biodiversity hotspot in central Chile using Landsat, BFAST and Landtrendr. International Geoscience and Remote Sensing Symposium (IGARS). Valencia, España, 22-27 July 2018.
 *	Labra, C., **Cabezas**, J. & C. Little. Delimitation of protection areas for water courses using hidrological modelling tools (2018). Joint conference on Forest and Water. Valdivia, Chile, 5-9 November 2018. (Original in Spanish)
 *	**Cabezas**, J., Fassnacht, F., Schmidt, T., Kleinschmit, B. & M. Foester. (2016) Satellite-based monitoring of invasive species in central-Chile: Detection of disturbances using Landsat time series. Presentation in the ForestSat 2016 congress. Santiago, Chile. 14-18 November 2016.
 *	**Cabezas**, J., Fassnacht, F., Schmidt, T., Kleinschmit,B. & M. Foester. (2016) Relating the disturbance history of natural vegetation in central Chile with the spread of three invasive species. Poster presented in “GEO BON Open Science Conference & All Hands Meeting 2016”. Leipzig, Germany. 4-8 de July 2016.
 *	Foester, M., Schmidt, T., Kleinschmit, B., Fassnacht, F & J. **Cabezas**. (2016) Detecting the spread of invasive tree species in central Chile with combined Landsat and Sentinel-2 data. Poster presented in “GEO BON Open Science Conference & All Hands Meeting 2016”. Leipzig, Germany. 4-8 de July 2016.
 *	**Cabezas**, J., Galleguillos M. & J. Pérez-Quezada. (2015). Prediction of the richness of vascular plants in a wetland of the Chiloe Island using remote sensing textural variables. Poster presented in the IV Congress of Native Flora, Concepción, Chile. 14-17 October 2015. (Original in Spanish)
 *	Pérez-Quezada, J., Brito, C., **Cabezas**, J., Salvo, P., Lemunao, P. Flores, E., Valdés, A., Fuentes, J.P., Galleguillos, M. & C. Pérez. (2015). Carbon stocks of an old-growth forest and an anthropogenic peatland in southern Chile. Poster presented in EGU 2015. Vienna, Austria. 12-17 April 2015.

# References

 *	Dr. Robert Waterworth. Director. The Mullion Group. e-mail: robert.waterworth@mulliongroup.com
 *	Dr. Fabian Fassnacht. Post-Doc Position. Institut für Geographie und Geoökologie, (Karlsruher Institut für Technologie, KIT). e-mail: fabian.fassnacht@kit.edu
 * 	Dr. Jorge Pérez Quezada, Associate Professor. Faculty of Agricultural Sciences (University of Chile). e-mail: jorgepq@uchile.cl


